---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SONIC

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/SONIC)](https://CRAN.R-project.org/package=SONIC)
[![R-CMD-check](https://github.com/christinasherpa24/SONIC/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/christinasherpa24/SONIC/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->




## Team Members

Christina Sherpa, Sariah Akhdar, Naomi Giancola

## Purpose

The purpose of this package is to provide information about the countries of the world. The functions serve two purposes. First, gain information about a specific country. Second, gain information about a specific issue for all countries (ex: abortion access or environmental issues).

## Target

The target audience for this package is anyone who is interested in facts about the world. Specifically, we are aiming to appeal to people who play games such as the Worldle and Globle. Additionally, this package can be used by people who are looking for information from all countries for a specific issue or issues surrounding a region (neighboring countries). 

## Installation

You can install the development version of sonic like so:

``` r
# install.packages("devtools")
devtools::install_github("christinasherpa24/sonic")
```


## Examples

Here are examples of how to run our functions and what they do. 

This is an example of the function **bordering_countries**. It allows users to enter a country name, for example "Albania" and then it will return a list of all the countries that border that country.

```{r ex1}
library(sonic)
bordering_countries("Albania")
```

The function **carbon_timeseries** takes in a country name such as "Nepal" and returns a line graph on the trend of carbon emissions throughout the years and also lists out the total carbon emissions.
```{r ex2}
library(sonic)
carbon_timeseries("Nepal")
```

The function **world_function** takes in a country name that a user inputs, and returns the population of the chosen country in 2000, 2010,2015 and 2020. 
```{r ex3}
library(sonic)
world_function("Algeria")
```

## Package Proposal 

We intend to create a package that will allow users to get information about a variety of issues for specific countries. So far, we have information about geography (bordering countries), carbon emissions, and population (from 2000-2022). We plan to add much more information such as women's rights which can include aspects such as a women's right to vote or access to abortion as well as LGBTQ+ matters. 

