---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# genworld

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/genworld)](https://CRAN.R-project.org/package=genworld)
[![R-CMD-check](https://github.com/christinasherpa24/SONIC/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/christinasherpa24/SONIC/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->




## Team Members

Christina Sherpa, Sariah Akhdar, Naomi Giancola

## Purpose

The purpose of this package is to provide information about different countries around the world. It includes data on various aspects of each country, such as the LGBTQ acceptance rate, COVID statistics, and Olympic participation. Users can use the package's functions to search for specific countries and learn more about them.

## Target

The target audience for this package is anyone who is interested in facts about the world. Specifically, we are aiming to appeal to people who play games such as the Worldle and Globle. Additionally, this package can be used by people who are looking for information from all countries for a specific issue or issues surrounding a region (neighboring countries). 

## Installation

You can install the development version of genworld like so:

``` r
# install.packages("devtools")
devtools::install_github("christinasherpa24/genworld")
```

## Included Datasets

We have a total of 8 datasets in this package: 

- `carbon_emissions` : Carbon emissions for every country from 1974 on wards
- `historical_olympics` : Historical Olympics data from 1896-2016
- `lgbtq_acceptance` : GAI (2,750 surveys conducted over 30 years) for countries
- `country_borders` : Information about countries that boarder each other
- `jewish_deaths` : Information pertaining to Jewish deaths in Europe from the Holocaust
- `world_population` : Information related to world population over the years for each country/region
- `covid_vaccinations` : Daily COVID vaccines administered in each country from 2020-onwards
- `covid_hospitalizations` : Daily COVID hospitalisations in each country from 2020-onwards 


## Examples

Here are examples of how to run our functions and what they do. 

This is an example of the function **bordering_countries**. It allows users to enter a country name, for example "Albania" and then it will return a list of all the countries that border that country.


The function **carbon_timeseries** takes in a country name such as "Nepal" and returns a line graph on the trend of carbon emissions throughout the years and also lists out the total carbon emissions.

```{r ex1}
library(genworld)
carbon_timeseries("Nepal")
```


```{r ex2}
library(genworld)
athlete_info("Nesar Ahmad Bahawi")
```


```{r ex3}
library(genworld)
team_medal_info("United States")
```


```{r ex4}
library(genworld)
sport_medal_info("United States", "Basketball")
```


```{r ex5}
library(genworld)
team_sport_medal_info("China")
```

Naomi's

This is an example of the function **countries_lgbt_acceptance**. It allows users to enter a country name, for example "France" and then it will outputthe GAI for that country, which indicates the acceptance of LGBTQ+ people

```{r ex6}
library(genworld)
countries_lgbt_acceptance("France")
```

This is an example of the function **lgbt_acceptance_graph**. It allows users to enter a country name, for example "France" and then it will output the graph of the GAI compared to the GAI's of other countries in the world. 

*Note: The graph is made using plotly which does not appear in ReadMe. To see the graph, please see the help file (?lgbt_acceptance_graph) and run the examples. 

```{r ex7}
library(genworld)
lgbt_acceptance_graph("France")
```


This is an example of the function **bordering_countries**. It allows users to enter a country name, for example “Albania” and then it will return a list of all the countries that border that country.

```{r ex8}
bordering_countries("Albania")
```


This is an example of the function **graph_jewish_killed**. It allows users to enter a country name, for example "France" and then it will return a bar chart of Jewish people killed during the Holocaust compared to the amount of Jewish people alive before the Holocaust.

*Note: The graph is made using plotly which does not appear in ReadMe. To see the graph, please see the help file (?graph_jewish_killed) and run the examples. 

```{r ex9}
library(genworld)
graph_jewish_killed("France")
```



The function **country_population** takes in a country name that a user inputs, and returns the population of the chosen country in 2000, 2010,2015 and 2022. 

```{r ex10}
library(genworld)
country_population('Algeria')
```


The function **daily_vaccinations_function** that takes in a country as an input and outputs the number of doses administered for the country chosen from 2020-present 
```{r ex11}
library(genworld)
daily_vaccinations_function('Algeria')
```



## Package Proposal 

We intend to create a package that will allow users to get information about a variety of issues for specific countries. So far, we have information about geography (bordering countries), carbon emissions, and population (from 2000-2022). We plan to add much more information such as women's rights which can include aspects such as a women's right to vote or access to abortion as well as LGBTQ+ matters. 
